%% Cover letter for Truelogic - Senior Full-stack Engineer (React/Node/TS)
%% Compile with: xelatex cover_truelogic.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your Senior Full-stack Engineer role is an exact match for what I do: React, Node.js, TypeScript, PostgreSQL, MongoDB, with REST APIs and CI/CD workflows. I have shipped production code in that exact stack for 5+ years.}

\lettercontent{Recent work: 50+ tailored web applications delivered in 12 months at Filltech, using TypeScript, Next.js, Node.js, Express, MongoDB Atlas, and AWS. I also built a multi-LLM AI chat platform (GPT Custom, Meta partnership) end-to-end: Next.js frontend, Node.js backend, PostgreSQL schema, AWS EC2 deployment, Cloudflare CDN in front.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Exact stack match:} React, Node.js, TypeScript, PostgreSQL, MongoDB --- 5+ years production
    \item \textbf{CI/CD workflows:} GitHub Actions, Docker, AWS deployments, Vercel
    \item \textbf{Agile/Scrum:} tight sprint cadence, 50+ apps in 12 months at Filltech
    \item \textbf{AI-native bonus:} have built AI products using your stack --- I use Claude Code and Cursor daily
\end{itemize}\par}
\vspace{6pt}

\lettercontent{What sets me apart from typical React/Node/TS candidates: I am also a CISSP-certified security practitioner and have built production AI products. So when your team is integrating AI features or dealing with security review, I have shipped that work, not just read about it.}

\lettercontent{My English is professional working proficiency, I am fully remote-friendly, and I have a track record of fast delivery. Available within 2--3 weeks.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
