\documentclass[]{cover}
\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}
\namesection{}{{\Huge{David Gonzalez}}}{%
\textbf{\href{mailto:davitcoin@pm.me}{davitcoin@pm.me}} \textbar{} +52 729 759 8371 \textbar{} \href{https://linkedin.com/in/david-gonzalez-7bb60921a}{LinkedIn} \textbar{} \href{https://github.com/dglezz1}{GitHub}%
}
\currentdate{\today}
\lettercontent{
Dear Hiring Manager,
\textbf{Self-taught software engineer with 5+ years shipping production LLM/RAG/full-stack systems. (ISC)² CISSP certified.}
I saw your posting for an AI Engineer who has shipped LLM-based assistants with RAG and tool-calling — that is exactly what I have been doing for the last two years.
At GPT Custom (Meta partnership), I shipped a multi-LLM chat platform orchestrating 10+ providers behind a single Next.js frontend, with personalized AI assistants and per-tenant model routing. At Filltech, I built the RAG layer for an AI legal chatbot from scratch: document ingestion, chunking, embeddings, vector retrieval, citation-grounded responses, and tenant isolation for confidential client data.
\begin{itemize}
  \item \textbf{Multi-LLM production experience:} 10+ provider orchestration (OpenAI, Anthropic, Meta) with per-tenant routing and cost optimization
  \item \textbf{RAG end-to-end:} enterprise legal chatbot with vector embeddings, document chunking, citation-grounded answers
  \item \textbf{Stack match:} TypeScript, Next.js, React, Node.js, PostgreSQL, AWS EC2, Cloudflare CDN — exactly your stack
  \item \textbf{Security-first default:} (ISC)² CISSP + ISO 27001 — I think about the threat model before the prompt
\end{itemize}
I live in Mexico City, fully remote-friendly across time zones, and available to start within 2–3 weeks. Portfolio at [github.com/dglezz1](https://github.com/dglezz1) including an active Studio (audio AI) project, openai-assistants reference, and a multi-LLM platform reference repo.
Open to a 30-minute conversation to walk through any of these projects.
I look forward to hearing from you.
}
\begin{flushright}
\closing{Sincerely,}
\signature{David Gonzalez}
\end{flushright}
\end{document}
