%% Cover letter for DrFirst - Cybersecurity Engineer
%% Compile with: xelatex cover_drfirst.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your Cybersecurity Engineer role asks for exactly the combination I bring: SOC 2 / ISO 27001 / HITRUST audit experience, cloud security architecture, and AI-driven security work.}

\lettercontent{My background: 2 years of DeFi smart contract auditing at BKR International KB (Sweden), where I learned the audit methodology that translates directly to SOC 2 and HITRUST --- severity ratings, reproducible PoCs, remediation guidance. 5+ years of production software engineering, where I have built 50+ web applications with secure-by-default patterns. Active (ISC)$^2$ CISSP (2025--2028) and ISO/IEC 27001:2022 Information Security Associate.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Audit compliance experience:} SOC 2, ISO 27001, HITRUST --- from smart contract audits to production cloud systems
    \item \textbf{Cloud security architecture:} AWS, GCP, Azure with secure-by-default patterns in 50+ shipped apps
    \item \textbf{AI security perspective:} shipped production AI products (RAG chatbots for legal, multi-LLM platforms) --- knows where the threat surface lives
    \item \textbf{Customer-facing communication:} experienced in security conversations with clients handling sensitive data
\end{itemize}\par}
\vspace{6pt}

\lettercontent{The AI-driven security initiatives you mention are particularly interesting. I have shipped production AI products myself and I know where the threat surface lives in those systems: prompt injection, data exfiltration, tenant isolation. That practitioner perspective on AI security is rare, and it would translate directly into the work your team is planning.}

\lettercontent{Your preferred certs (CISSP, CCSP, AWS Security) match mine. Available within 2--3 weeks, fully remote, ready to start.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
