%% Cover letter for Chicory AI - AI Agents / LLM Engineer
%% Compile with: xelatex cover_chicory.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your AI Agents / LLM Engineer role at Chicory is a direct match for what I have been building. You are looking for an engineer with hands-on LLM and AI agent experience, including multi-agent systems, ontologies, knowledge graphs, and RAGs. I have shipped all of these in production.}

\lettercontent{Most relevant: I built a multi-LLM chat platform at GPT Custom orchestrating 10+ providers behind a unified Next.js frontend, with personalized AI assistants. I built the RAG layer for an AI legal chatbot at Filltech: document ingestion, chunking, embeddings, vector retrieval, citation-grounded answers, and tenant-isolated data stores for confidential client data.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Multi-LLM production experience:} 10+ provider orchestration behind unified UX
    \item \textbf{RAG end-to-end:} embeddings, vector retrieval, citation-grounded answers
    \item \textbf{Strong software engineering foundation:} Next.js, React, Node.js, PostgreSQL, AWS
    \item \textbf{Bias for action:} 50+ apps in 12 months, full stack ownership, debug at OS layer
\end{itemize}\par}
\vspace{6pt}

\lettercontent{The bias-for-action piece: I am a really good software engineer who happens to specialize in AI products. TypeScript, Next.js, React, Node.js, PostgreSQL, AWS EC2, Cloudflare CDN --- I own the full stack. When the agent stack breaks at the OS layer or the database layer or the network layer, I debug. I do not need to call a separate team.}

\lettercontent{Active (ISC)$^2$ CISSP and ISO 27001 mean I think about the threat model in agent systems: prompt injection, data exfiltration, tenant boundaries --- before the prompt is even written.}

\lettercontent{Available within 2--3 weeks, fully remote, comfortable with US Pacific time collaboration.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
