%% Cover letter for DESIGN & DESKTOP - Fullstack Software Developer
%% Compile with: xelatex cover_desktop.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your fullstack role requires a TypeScript-first stack (Next.js, Hono, Drizzle ORM, PostgreSQL, Bun), AI-native development practices, and an ownership mindset. I tick every one of those boxes.}

\lettercontent{My recent stack: TypeScript + Next.js + React + Node.js + Express, with MongoDB Atlas and PostgreSQL in production, AWS EC2 deployments, and Cloudflare CDN. I have used Hono, Drizzle, and Bun in personal projects and would ramp up fast. I use Claude Code daily in my workflow.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Production cadence:} 50+ web applications in 12 months at Filltech, multi-LLM platform at GPT Custom
    \item \textbf{TypeScript-first experience:} Next.js, React, Node.js, Express, Prisma, Hono (learning Drizzle/Bun)
    \item \textbf{AI-native development:} Claude Code, Cursor, used daily
    \item \textbf{AI product experience:} have built the AI products your team integrates with
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Production cadence: 50+ web applications in 12 months at Filltech. Multi-LLM chat platform at GPT Custom. RAG chatbot for legal professionals. POS systems, e-commerce, insurance apps --- I have shipped across enough domains to know when to follow the standard pattern and when to break it.}

\lettercontent{The AI-native piece is my differentiator. I have built the AI products your team is integrating with: multi-LLM orchestration, RAG, AI agents. So when the team hits a ``this AI feature is hard'' problem, I have solved it before, not just researched it.}

\lettercontent{Available immediately, fully remote, comfortable with high-pace, high-ownership culture.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
