%% Cover letter for Lennar - Senior Cloud Security Engineer
%% Compile with: xelatex cover_lennar.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your Senior Cloud Security Engineer role asks for 5+ years of cloud security engineering across AWS and Azure --- exactly the experience I bring, with the added bonus of an active (ISC)$^2$ CISSP and ISO 27001.}

\lettercontent{What I have shipped: production services on AWS EC2 with Cloudflare WAF in front, secure-by-default patterns (parameterized queries, least-privilege IAM, encrypted-at-rest storage), 50+ web applications deployed in 12 months. I have designed tenant-isolated data stores for AI products handling sensitive legal data, with strict data boundaries.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Certifications match:} CISSP (active 2025--2028), ISO 27001:2022, AWS Cloud Cybersecurity
    \item \textbf{Multi-cloud fluency:} AWS, GCP, Azure --- deployed production workloads on all three
    \item \textbf{DevSecOps integration:} secure SDLC baked into my daily work as the engineer building the systems
    \item \textbf{Frameworks:} NIST, ISO 27001, CIS Controls --- worked inside all three in production
\end{itemize}\par}
\vspace{6pt}

\lettercontent{I am at the edge of your 5+ year requirement (5+ total) but the depth of cert + hands-on cloud security work makes it a strong match. The DevSecOps piece (SAST/DAST, vulnerability remediation, SDLC security) is integrated into my daily work because I am the engineer building the systems --- not a separate team reviewing them.}

\lettercontent{SIEM, vulnerability management, NIST/ISO 27001/CIS frameworks are all in my regular practice. Fully remote, available within 2--3 weeks.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
