%% Cover letter for Armis Security - Cybersecurity Analyst
%% Compile with: xelatex cover_armis.tex

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{David Gonzalez}}{  \href{mailto:davitcoin@pm.me}{davitcoin@pm.me} | +52 729 759 8371 |  \urlstyle{same}\href{https://github.com/dglezz1}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Manager,}

\lettercontent{Your Cybersecurity Analyst role on the GRC team at Armis is a strong match for my background. I hold an active (ISC)$^2$ CISSP and ISO/IEC 27001:2022 Information Security Associate, with hands-on production experience in audit, compliance, and secure-by-default engineering.}

\lettercontent{What I have done that maps to your day-to-day: I have run line-by-line code reviews of production DeFi smart contracts (BKR International KB, Sweden), identifying critical vulnerabilities across reentrancy, access-control, and oracle manipulation. I have shipped 50+ production web applications (Filltech) with secure-by-default patterns: parameterized queries, hardened auth flows, least-privilege IAM, encrypted-at-rest storage. And I have designed tenant-isolated AI products handling confidential legal documents with strict data boundaries.}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Certifications match your preferred path:} CISSP (current, 2025--2028), ISO 27001:2022, Google Cloud Cybersecurity, Ethical Hacking
    \item \textbf{Framework experience:} ISO, SOC, HIPAA, NIST --- have worked inside these in production
    \item \textbf{Audit methodology:} severity ratings, reproducible PoCs, remediation guidance (from 2 years of DeFi smart contract auditing)
    \item \textbf{Comfortable with customer-facing security work} --- built AI products for legal clients with strict data requirements
\end{itemize}\par}
\vspace{6pt}

\lettercontent{I am a security practitioner who also builds the systems. That combination is rare at this level, and it means I can both gather the evidence you need for SOC 2 / ISO audits and design the controls that make those audits go smoothly.}

\lettercontent{Available to start within 2--3 weeks, fully remote, and comfortable working with North American teams.}

\lettercontent{I look forward to hearing from you.}

\begin{flushright}
\closing{Sincerely,}

\signature{David Gonzalez}
\end{flushright}
\end{document}
