%% Master CV for David Gonzalez
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_david.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={David Gonzalez - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{David}{Gonzalez}
\address{Mexico City, Mexico}{}{}
\phone[mobile]{+52 729 759 8371}
\email{davitcoin@pm.me}
\extrainfo{\href{https://linkedin.com/in/david-gonzalez-7bb60921a}{LinkedIn}, \href{https://github.com/dglezz1}{GitHub}, \href{https://davitcoin.net}{Portfolio}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Software engineer with 5+ years of experience spanning AI/LLM engineering, cybersecurity, and full-stack development. Combines production-grade engineering (Next.js, TypeScript, Python, AWS) with security-first design (CISSP, ISO 27001, smart contract auditing, systems-level C). Most recent work includes a multi-LLM chat platform with 10+ providers, an enterprise RAG chatbot for legal professionals, and 50+ production web applications. Open to remote AI/LLM, cybersecurity, and full-stack roles worldwide.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{AI / LLM Engineering}: Multi-LLM orchestration (OpenAI, Anthropic, Meta, open-weight), RAG pipelines, vector embeddings, prompt engineering, AI agents, OpenAI Assistants API.

\item \textbf{Cybersecurity}: Smart contract auditing (Solidity / EVM), OWASP Top 10, vulnerability analysis, application security, ethical hacking, ISO 27001, CISSP-aligned controls.

\item \textbf{Full-Stack Development}: TypeScript, Next.js, React, Node.js, Express, NestJS, Remix, Prisma ORM, MongoDB, PostgreSQL, MySQL.

\item \textbf{Cloud \& Infrastructure}: AWS (EC2, S3, IAM, CloudFront), GCP, Azure, Cloudflare WAF/CDN, Docker, containerized deployments.

\item \textbf{Systems \& Tooling}: C / C++ for kernel-adjacent code, Bash, Git, GitHub, Burp Suite, Metasploit, Nessus, Nmap, Wireshark.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{2024--Present}{Full Stack Developer}{Filltech}{Mexico City, Mexico (Remote)}{}{\vspace{1pt}
\begin{itemize}
    \item Delivered 50+ tailored websites and web applications in 12 months across diverse client industries.
    \item Built an enterprise-grade RAG chatbot for legal professionals with document vectorization, tenant-isolated data stores, and source-cited answers.
    \item Built production e-commerce backends (MongoDB Atlas, Node.js, Express, React) with secure-by-default patterns.
    \item Operated production services on AWS EC2 with Cloudflare CDN, parameterized queries, least-privilege IAM, encrypted-at-rest storage.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{2023--2024}{Full Stack Developer, LLM Platform}{GPT Custom}{Remote (Meta partnership)}{}{\vspace{1pt}
\begin{itemize}
    \item Architected and shipped a multi-LLM AI chat platform supporting 10+ providers behind a unified Next.js UX.
    \item Built WhatsApp Business API integration with custom training and persistent conversation state in PostgreSQL.
    \item Owned the full stack end-to-end: Next.js frontend, Node.js backend, PostgreSQL schema, AWS EC2 deployment, Cloudflare CDN.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role ---
\item{\cventry{2022--2023}{Smart Contract Auditor}{BKR International KB}{Remote (Sweden, DeFi)}{}{\vspace{1pt}
\begin{itemize}
    \item Line-by-line Solidity code review for DeFi protocols pre-mainnet deployment.
    \item Identified critical vulnerabilities: reentrancy, access-control bypass, oracle manipulation, unsafe external calls.
    \item Produced severity-rated audit reports with reproducible PoCs and concrete remediation guidance.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Continuous}{Self-Taught Software Engineer}{}{}{}{\vspace{1pt}
Continuous learning through OSS contributions, certifications (CISSP, ISO 27001, Google Cloud Cybersecurity), and 5+ years of production engineering. Active GitHub presence (30+ repositories) including systems-level C work, AI applications, and Web3.
}}

\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{(ISC)\textsuperscript{2} CISSP} -- Certified Information Systems Security Professional (2025--2028)
\item \textbf{ISO/IEC 27001:2022} Information Security Associate (2025--Present)
\item \textbf{Google Cloud Cybersecurity} (2026--2029)
\item \textbf{Google Foundations of Cybersecurity} (2019--Present)
\item \textbf{Cybersecurity Analyst Skill Path} -- Google (2024)
\item \textbf{Ethical Hacking Course} -- Codecademy (2024)
\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (fluent, professional working proficiency).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{1st place} -- Near Protocol Web3 Hackathon (2021).}
\item{\textbf{1st place} -- Internet Computer Protocol (ICP) Web3 Community Hackathon (2021).}
\item{\textbf{1st place} -- Open Web Academy Hackathon (2021).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
