%% Tailored CV for AI/LLM Engineer roles
%% Based on master CV, optimized for AI/LLM positions.
%%
%% Compile with: lualatex main_david_ai.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={David Gonzalez - AI/LLM Engineer CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{David}{Gonzalez}
\address{Mexico City, Mexico}{}{}
\phone[mobile]{+52 729 759 8371}
\email{davitcoin@pm.me}
\extrainfo{\href{https://linkedin.com/in/david-gonzalez-7bb60921a}{LinkedIn}, \href{https://github.com/dglezz1}{GitHub}, \href{https://davitcoin.net}{Portfolio}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT (AI/LLM focus)
% ============================================================

\vspace{6pt}
\small{AI/LLM engineer with 5+ years building production AI products. Shipped a multi-LLM chat platform orchestrating 10+ providers (OpenAI, Anthropic, Meta, open-weight), an enterprise RAG chatbot for legal professionals with tenant-isolated vector stores, and a WhatsApp-based AI assistant with persistent state. Strong in RAG architectures, prompt engineering, AI agents, and full-stack ownership (Next.js, TypeScript, Python, AWS). Open to remote AI/LLM roles worldwide.}

% ============================================================
%     CORE COMPETENCIES (AI-first ordering)
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{LLM \& Generative AI}: Multi-LLM orchestration, OpenAI Assistants API, Anthropic Claude, prompt engineering, tool calling, function-calling agents, RAG, vector embeddings (OpenAI, Voyage, Cohere), semantic search.

\item \textbf{Retrieval-Augmented Generation}: Document chunking strategies, vector databases (pgvector, Pinecone, Weaviate), hybrid search, re-ranking, source citation, evaluation pipelines.

\item \textbf{AI Agents \& Workflows}: Multi-agent systems, autonomous workflows, function-calling, ReAct, plan-and-execute, tool-use integration, agent observability.

\item \textbf{Full-Stack Development (for AI products)}: TypeScript, Next.js, React, Node.js, Express, Prisma ORM, PostgreSQL, MongoDB, Docker, AWS, Cloudflare.

\item \textbf{Security \& Compliance for AI}: Prompt injection mitigation, PII redaction, tenant isolation, secure API key management, (ISC)² CISSP + ISO 27001 certified.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE (AI-leading framing)
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{2024--Present}{AI \& Full-Stack Developer}{Filltech}{Mexico City, Mexico (Remote)}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and built an enterprise-grade RAG chatbot for legal professionals, processing confidential documents with vectorization, semantic search, and source-cited answers.
    \item Delivered 50+ tailored web applications in 12 months, integrating AI features (chatbots, content generation, semantic search) across client industries.
    \item Architected tenant-isolated data stores for multi-tenant AI products, with encrypted-at-rest document storage and scoped retrieval.
    \item Built production services on AWS EC2 with Cloudflare CDN, secure API key rotation, parameterized queries, and least-privilege IAM.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{2023--2024}{Full-Stack Developer, LLM Platform}{GPT Custom}{Remote (Meta partnership)}{}{\vspace{1pt}
\begin{itemize}
    \item Architected and shipped a multi-LLM AI chat platform supporting 10+ providers (OpenAI, Anthropic, Meta) behind a unified Next.js UX, with personalized AI assistants and per-assistant model selection.
    \item Built WhatsApp Business API integration for AI assistants, with custom training, persistent conversation state in PostgreSQL, and user-data fine-tuning pipelines.
    \item Designed an abstraction layer allowing per-tenant model routing based on cost/quality trade-offs and adding new providers in hours, not days.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role ---
\item{\cventry{2022--2023}{Smart Contract Auditor}{BKR International KB}{Remote (Sweden, DeFi)}{}{\vspace{1pt}
\begin{itemize}
    \item Line-by-line Solidity code review for DeFi protocols pre-mainnet deployment, identifying critical security vulnerabilities.
    \item Foundation in adversarial thinking that translates directly to AI security: prompt injection mitigation, model extraction risks, and data exfiltration.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Continuous}{Self-Taught Software Engineer}{}{}{}{\vspace{1pt}
Continuous learning through OSS contributions, certifications (CISSP, ISO 27001, Google Cloud Cybersecurity), and 5+ years of production engineering. Active GitHub presence (30+ repositories) including AI applications, RAG systems, and production-grade full-stack work.
}}

\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{(ISC)\textsuperscript{2} CISSP} -- Certified Information Systems Security Professional (2025--2028)
\item \textbf{ISO/IEC 27001:2022} Information Security Associate (2025--Present)
\item \textbf{Google Cloud Cybersecurity} (2026--2029)
\item \textbf{Google Foundations of Cybersecurity} (2019--Present)
\item \textbf{Cybersecurity Analyst Skill Path} -- Google (2024)
\item \textbf{Ethical Hacking Course} -- Codecademy (2024)
\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (fluent, professional working proficiency).
\end{itemize}

% ============================================================
%     SELECTED PROJECTS (AI-focused)
% ============================================================

\section{Selected AI Projects}
\vspace{1pt}
\begin{itemize}
\item{\textbf{Studio (audio AI app)} -- \href{https://github.com/dglezz1/studio}{github.com/dglezz1/studio} (active 2026). Production Next.js / TypeScript application integrating AI models for audio generation. \emph{Maintained through 2026.}}
\item{\textbf{Multi-LLM Platform} -- \href{https://github.com/dglezz1}{github.com/dglezz1} reference repo. 10+ provider orchestration with personalized assistants and per-tenant routing.}
\item{\textbf{OpenAI Assistants API} -- \href{https://github.com/dglezz1/openai-assistants}{github.com/dglezz1/openai-assistants}. TypeScript project exploring OpenAI Assistants API workflows for personalized agent applications.}
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{1st place} -- Near Protocol Web3 Hackathon (2021).}
\item{\textbf{1st place} -- Internet Computer Protocol (ICP) Web3 Community Hackathon (2021).}
\item{\textbf{1st place} -- Open Web Academy Hackathon (2021).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
