%% Tailored CV for Cybersecurity / Cloud Security roles
%% Based on master CV, optimized for security positions.
%%
%% Compile with: lualatex main_david_cyber.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={David Gonzalez - Cybersecurity Analyst CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{David}{Gonzalez}
\address{Mexico City, Mexico}{}{}
\phone[mobile]{+52 729 759 8371}
\email{davitcoin@pm.me}
\extrainfo{\href{https://linkedin.com/in/david-gonzalez-7bb60921a}{LinkedIn}, \href{https://github.com/dglezz1}{GitHub}, \href{https://davitcoin.net}{Portfolio}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT (Cybersecurity focus)
% ============================================================

\vspace{6pt}
\small{(ISC)\textsuperscript{2} CISSP-certified cybersecurity analyst with hands-on experience across smart contract auditing, application security, and multi-cloud environments. Background combines 2 years of DeFi smart contract auditing (BKR International, Sweden), offensive security training (Ethical Hacking, Google Cybersecurity Analyst), and production software engineering (50+ web apps at Filltech). Holds ISO/IEC 27001:2022 Information Security Associate. Open to remote cybersecurity, GRC, and cloud security roles worldwide.}

% ============================================================
%     CORE COMPETENCIES (Security-first ordering)
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Certifications \& Compliance}: (ISC)² CISSP (2025--2028), ISO/IEC 27001:2022 Associate, Google Cloud Cybersecurity, Google Foundations of Cybersecurity, Cybersecurity Analyst Skill Path (Google).

\item \textbf{Application \& Cloud Security}: OWASP Top 10, API security, secure SDLC, AWS / GCP / Azure security posture, Cloudflare WAF, multi-cloud IAM, least-privilege access.

\item \textbf{Smart Contract \& Web3 Security}: Solidity / EVM auditing, DeFi vulnerability analysis (reentrancy, access-control, oracle manipulation), severity-rated reporting with PoCs, on-chain threat modeling.

\item \textbf{Offensive Security Tooling}: Burp Suite, Metasploit, Nessus, Nmap, Wireshark, Cisco XDR, Azure Security Center, Python scripting for automation.

\item \textbf{Systems-Level Security}: C / C++ for kernel-adjacent code (ARM64 driver projects), memory safety, low-level attack surfaces, supply-chain review.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE (Security-leading framing)
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{2024--Present}{Full-Stack Developer (Secure-by-Default)}{Filltech}{Mexico City, Mexico (Remote)}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and built an enterprise RAG chatbot for legal professionals, with tenant-isolated data stores, encrypted-at-rest document storage, and scoped retrieval — security-first patterns for AI products handling sensitive data.
    \item Delivered 50+ production web applications in 12 months, applying secure-by-default design: parameterized queries, hardened auth flows, least-privilege cloud IAM, encrypted storage.
    \item Operated production services on AWS EC2 with Cloudflare WAF, secrets management, and secure API key rotation patterns.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{2023--2024}{Full-Stack Developer, LLM Platform}{GPT Custom}{Remote (Meta partnership)}{}{\vspace{1pt}
\begin{itemize}
    \item Built a multi-LLM chat platform with secure API key management across 10+ providers, request signing, and rate-limit handling.
    \item Implemented prompt-injection mitigation patterns for WhatsApp-based AI assistants exposed to untrusted user input.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role (security-first) ---
\item{\cventry{2022--2023}{Smart Contract Auditor}{BKR International KB}{Remote (Sweden, DeFi)}{}{\vspace{1pt}
\begin{itemize}
    \item Line-by-line Solidity code review for DeFi protocols pre-mainnet deployment, identifying critical vulnerabilities (reentrancy, access-control bypass, oracle manipulation, unsafe external calls).
    \item Produced severity-rated audit reports (Critical / High / Medium / Low) with reproducible PoCs and concrete remediation guidance.
    \item Collaborated with engineering teams on secure remediation patterns and post-fix re-verification.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Continuous}{Self-Taught Security Engineer}{}{}{}{\vspace{1pt}
Continuous learning through hands-on security work, certifications (CISSP, ISO 27001, Google Cloud Cybersecurity), and 5+ years building and auditing production systems. Active GitHub presence (30+ repositories) including systems-level C security work, smart contract code, and pentesting tools.
}}

\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{(ISC)\textsuperscript{2} CISSP} -- Certified Information Systems Security Professional (2025--2028)
\item \textbf{ISO/IEC 27001:2022} Information Security Associate (2025--Present)
\item \textbf{Google Cloud Cybersecurity} (2026--2029)
\item \textbf{Google Foundations of Cybersecurity} (2019--Present)
\item \textbf{Cybersecurity Analyst Skill Path} -- Google (2024)
\item \textbf{Ethical Hacking Course} -- Codecademy (2024)
\end{itemize}

% ============================================================
%     SECURITY PROJECTS
% ============================================================

\section{Selected Security Projects}
\vspace{1pt}
\begin{itemize}
\item{\textbf{iOS Pentesting Toolkit} -- \href{https://github.com/dglezz1/Ios-pentesting}{github.com/dglezz1/Ios-pentesting}. Python-based iOS application security testing (runtime analysis, jailbreak detection, attack surface mapping).}
\item{\textbf{ARM64 Driver (kernel-level C)} -- \href{https://github.com/dglezz1/AX900-driver-for-ARMx64}{github.com/dglezz1/AX900-driver-for-ARMx64}. Memory management, hardware interfaces, minimal-runtime code paths — useful for firmware and supply-chain review.}
\item{\textbf{Blockchain-Smartcontracts} -- \href{https://github.com/dglezz1/Blockchain-Smartcontracts}{github.com/dglezz1/Blockchain-Smartcontracts}. Sustained engagement with Web3 attack surfaces and EVM security patterns.}
\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (fluent, professional working proficiency).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{1st place} -- Near Protocol Web3 Hackathon (2021).}
\item{\textbf{1st place} -- Internet Computer Protocol (ICP) Web3 Community Hackathon (2021).}
\item{\textbf{1st place} -- Open Web Academy Hackathon (2021).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
